Homework 1 - [Your team name here]
========================================================

### Implementation

<!--
Use this section to implement the fizzbuzz function.

This should include a short write up describing your approach
to implementing the function. Not both code formating / style
and your writeup matter for your overall grade.
-->
The code works by taking in any vector argument of floats and then iterates through all of the arguments in sequential order.
Then it checks if the indices of the vector are divisible by 3, 5, or 15. It then replaces those values with the respective word.
Lastly I print out everything thus retrieving the results line by line. 

```{r}

FizzBuzz = function(v){
  a=v
  for ( i in 1:length(v)){
    if (v[i]%%3==0 && v[i]%%5!=0)
      a[i]="Buzz"
    if (v[i]%%3!=0 && v[i]%%5==0)
      a[i]="Fizz"
    if (v[i]%%15==0)
      a[i]="FizzBuzz"
    
  }
  for( j in 1:length(a)){
    print(a[j])
  }
}
```

### Output

<!--
Use this section to show the output of your 
fizzbuzz function for integer values from 30 to 50.

No writeup is necessary for this section.
-->
[1] "FizzBuzz"
[1] "31"
[1] "32"
[1] "Buzz"
[1] "34"
[1] "Fizz"
[1] "Buzz"
[1] "37"
[1] "38"
[1] "Buzz"
[1] "Fizz"
[1] "41"
[1] "Buzz"
[1] "43"
[1] "44"
[1] "FizzBuzz"
[1] "46"
[1] "47"
[1] "Buzz"
[1] "49"
[1] "Fizz"

```{r}
FizzBuzz(30:50)
```